### 2017-03-14 CO750-ApproximationAlgorithmsTopics/assignments/assignment_02.tex
finished typing 6

Now we consider Case $2$. Suppose $Z_i$ is a $k$-restricted star where $k \in \{3,4\}$. Then with probability $\frac{1}{k}$ (when $e$ is the edge not in $\tilde{B}$), $|W(e)| = k-1$. With probability $1-\frac{1}{k}$), $|W(e)| = 1$. Thus by lemma \ref{lemma:20} we have

@@

&= (\frac{3}{5} + \frac{2}{10}) M \\
&= (\frac{8}{10})M \\
&= \frac{4}{5}M.

@@

%Q6
\section{}
\end{document}

>>>>

Now we consider Case $2$. Suppose $Z_i$ is a $k$-restricted star where $k \in \{3,4\}$. Then with probability $\frac{1}{k}$ (when $e$ is the edge not in $\tilde{B}$), $|W(e)| = k-1$. With probability $(1-\frac{1}{k}$), $|W(e)| = 1$. Thus by lemma \ref{lemma:20} we have

@@

&= (\frac{3}{5} + \frac{3}{5}) M \\
&= (\frac{6}{5})M \\
&\leq \frac{5}{4}M.

@@

%Q6
\section{}
\paragraph{}
In the metric Travelling Salesman Problem $(TSP)$ we are given a metric graph $G=(V,E)$ with edge costs $c: E\rightarrow \R_+$. The goal is to find a minimum cost Hamilton Cycle visiting each $v \in V$. The Held-Karp relaxation for $(TSP)$, denoted $(HK)$ is
\begin{align*}
\min \sum_e c(e) x_e& \\
\text{s.t.} x(\delta(v)) &= 2 &\forall v \in V \\
x(\delta(S)) &\geq 2 &\forall S \subseteq V \\
x &\geq 0.
\end{align*}
Let $n = |V|$. Let $x$ be a basic solution to $(HK)$. Our goal is to show that $x$ has $O(n)$ non-zero variables. The number of variables in $x$ correspond to a maximum size set of linearly independent tight constraints. Therefore the non-zero variables correspond to a collection $\cL \subseteq 2^V$ such that $x(\delta(S) = 2$ for all $S \in \cL$, and $\{\chi(S): S \in \cL\}$ is maximal linearly independent and $\chi(S)$ denotes the incidence vector of $S$. Hence we need to show that $|\cL| = O(n)$.
\paragraph{}
The constant function $f: 2^V \rightarrow \{2\}$ is trivially weakly supermodular. Therefore we may invoke a theorem from class saying we may choose $\cL$ to be a laminar family.
\paragraph{}
To show $|\cL| = O(n)$ we proceed by induction on $|V|$, the size of the ground set. The claim is trivial for $|V| = 1$: $|\cL| \leq |V|  = O(n)$. Suppose $|V| >1$. For the inductive hypothesis suppose for all $V' \subseteq V$, any laminar family on ground set $V'$ has size $O(|V'|)$. Let $S \in \cL\backslash\{V\}$ such that $|S|$ is maximal. We may assume such $S$ exists, as otherwise $|\cL| = 1 = O(n)$ as desired. Since $\cL$ is laminar, for all $S' \in \cL \backslash \{V\}$ either $S' \subseteq S$ or $S' \cap S = \emptyset$. Let $\cL' = \{ S' \in \cL\backslash\{V\} : S' \subseteq S\}$ and let $\cL'' = \{S' \in \cL\backslash \{V\} : S'\cap S \neq \emptyset\}$. Since $\cL'$ and $\cL''$ are subsets of $\cL$ they are both laminar families. The ground set of $\cL'$ is $S$, and the ground set of $\cL''$ is $V\backslash S$. Therefore by the inductive hypothesis $|\cL'| = O(|S|)$ and $|\cL''| = O(|V\backslash S|)$. Also, $\cL \subseteq \{V\} \cup \cL' \cup \cL''$. Then 
$$|\cL| \leq |\{V\}| + |\cL'| + |\cL''| = 1 + O(|S|) + O(|V\backslash S|) = O(|V\backslash S| + |S| + 1) = O(|V|).$$
Hence by induction $|\cL| = O(n)$ as desired. $\blacksquare$
\end{document}
